Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-08-07 cordillera-cycle.tex
Switch to print layout for thesis.
Pull figures up in the text.

% Copernicus manuscript
\documentclass[tc, manuscript]{copernicus}

% Copernicus final print
%\documentclass[tc]{copernicus}

@@

% =============================================================================
\begin{document}
\linenumbers
% =============================================================================

@@

@@

The PDD computation accounts for stochastic temperature variations by assuming
a normal temperature distribution of standard deviation $\sigma$ aroung the
expected value $T_m$. It is expressed by an error-function formulation
\citep{Calov.Greve.2005},
\begin{equation}
    \label{eqn:calovgreve}
    \mathrm{PDD} = \int_{t_1}^{t_2} \mathrm{d}t
        \left[\frac{\sigma}{\sqrt{2\pi}}
                \exp\left({-\frac{T_{m}^2}{2\sigma^2}}\right)
              + \frac{T_{m}}{2} \, \mathrm{erfc}
                \left(-\frac{T_{m}}{\sqrt{2}\sigma}\right)\right] \,,
\end{equation}
which is numerically approximated using week-long sub-intervals. In order to
account for the effects of spatial and seasonal variations of temperature
variability \citep{Seguinot.2013}, $\sigma$ is computed from daily temperature
values from the NARR, after excluding variability associated
with the seasonal cycle itself \citep[cf.][]{Seguinot.Rogozhina.2014}.
Degree-day factors for snow and ice melt are derived from
mass-balance measurements on contemporary glaciers from the Coast Mountains and
Rocky Mountains in British Columbia
\citep[Table~\ref{tab:params};][]{Shea.etal.2009}.

Temperature offset time-series, ${\Delta}T_{TS}$, are derived from
palaeo-temperature proxy records from
the Greenland Ice Core Project \citep[GRIP,][]{Dansgaard.etal.1993}, the
North Greenland Ice Core Project \citep[NGRIP,][]{Andersen.etal.2004},
the European Project for Ice Coring in Antarctica \citep[EPICA,][]
{Jouzel.etal.2007}, the Vostok ice core \citep{Petit.etal.1999}, and Ocean
Drilling Program (ODP) sites 1012 and 1020, both located off the coast of
California \citep{Herbert.etal.2001}. Palaeo-temperatures from the GRIP and
NGRIP
records were calculated from oxygen isotope (\chem{\delta^{18}O}) measurements
using a quadratic equation \citep{Johnsen.etal.1995},
\begin{equation}
    {\Delta}T_{TS}(t) = -11.88 [\chem{\delta^{18}O}(t)
                               -\chem{\delta^{18}O}(0)]
                        -0.1925[\chem{\delta^{18}O}(t)^2
                                -\chem{\delta^{18}O}(0)^2] \,,
\end{equation}
while temperature reconstructions from Antarctic and oceanic cores were
provided as such. All records were scaled linearly (Table~\ref{tab:records}) in
order to simulate comparable ice extents at the LGM  (Table~\ref{tab:extrema})
and realistic outlines (Fig.~\ref{fig:snapshots}).

% tab:params
\begin{table*}
  \centering
  \caption{Parameter values used in the ice sheet model.}
  \label{tab:params}
  {\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline

@@

% tab:records
\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22~ka after scaling.}
  \label{tab:records}
  {\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (m~a.s.l) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree} 35' N  % 72.58 (decimal)
             &  37{\degree} 38' W  % 37.64 (decimal)
             & 3238\,m
             & \chem{\delta^{18}O}
             & 0.35 & -5.8{\degree}C  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

@@

% tab:extrema
\begin{table*}[t]
  \caption{Extremes in Cordilleran ice sheet volume and extent corresponding to
           MIS~4, 3 and 2 for each of the six low-resolution simulations
           (Fig.~\ref{fig:timeseries}).}
  \label{tab:extrema}
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.58 &  49.24 &  19.52
             &   1.98 &   0.46 &   2.13
             &   7.52 &   0.89 &   8.52 \\
    NGRIP    &  60.26 &  50.16 &  22.85
             &   2.16 &   0.50 &   2.09
             &   8.69 &   0.93 &   8.24 \\
    EPICA    &  61.87 &  45.57 &  17.10
             &   1.57 &   0.95 &   2.08
             &   5.20 &   2.44 &   8.35 \\
    Vostok   &  60.87 &  49.68 &  16.87
             &   1.55 &   0.86 &   2.14
             &   5.10 &   2.01 &   8.66 \\
    ODP 1012 &  55.41 &  47.08 &  23.21
             &   1.44 &   0.85 &   2.13
             &   4.50 &   2.06 &   8.46 \\
    ODP 1020 &  60.16 &  52.24 &  29.46
             &   1.32 &   0.70 &   2.08
             &   3.88 &   1.52 &   8.32 \\
    \middlehline
    Minimum  &  61.87 &  52.24 &  29.46
             &   1.32 &   0.46 &   2.08
             &   3.88 &   0.89 &   8.24 \\
    Maximum  &  55.41 &  45.57 &  16.87
             &   2.16 &   0.95 &   2.14
             &   8.69 &   2.44 &   8.66 \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

% avoid "too many unprocessed floats" errors
\clearpage

% fig:locmap
\begin{figure}
  \includegraphics{locmap}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas once covered by the Cordilleran (CIS), Laurentide (LIS),
           Innuitian (IIS) and Greenland (GIS) ice sheets during the last
           18\,\unit{\chem{^{14}C}\,ka} (21.4\,cal\,ka)
           \citep{Dyke.2004}. The rectangular box denotes the location of the
           modelling domain used in this study. Major mountain ranges covered
           by the ice sheet include the Alaska Range (AR), the Wrangell and
           St.-Elias mountains (WSEM), the Selwyn and Mackenzie mountains
           (SMKM), the Skeena Mountains (SM), the Coast and Rocky
           Mountains (CRM) and the North Cascades (NC). Major depressions
           include the Liard Lowland (LL), the Interior Plateau of British
           Columbia (IP) and the Puget Lowland (PL). The background
           map consists of ETOPO1 \citep{Amante.Eakins.2009} and Natural Earth
           Data \citep{Patterson.Kelso.2014}.}
  \label{fig:locmap}
\end{figure}

% fig:atm
\begin{figure}
  \includegraphics{atm}
  \caption{Monthly mean near-surface air temperature, precipitation and
           standard deviation of daily mean temperature for January and July
           from the North American Regional Reanalysis
           \citep[NARR;][]{Mesinger.etal.2006},
           used to force the ice sheet model. Note the
           strong contrasts in seasonality, timing of the precipitation peak,
           and temperature variability over the model domain, notably between
           coastal and inland regions.}
  \label{fig:atm}
\end{figure}

% fig:timeseries
\begin{figure*}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and ocean records
           (Table~\ref{tab:records}) used as palaeo-climate forcing for the ice
           sheet model (top panel), and modelled ice volume (bottom panel)
           through the last 120\,ka. Ice volumes are expressed in meters of sea
           level equivalent (m~s.l.e.). Gray fields indicate Marine Oxygen
           Isotope Stage (MIS) boundaries for MIS~2 and MIS~4 according to a
           global compilation of benthic \chem{\delta^{18}O} records
           \citep{Lisiecki.Raymo.2005}. Hatched rectangles highlight the
           time-volume space for ice volume extremes corresponding to MIS~4
           (61.9--55.4\,ka), MIS~3 (52.2--45.6\,ka), and MIS~2 (LGM,
           29.5--16.9\,ka). Dotted lines correspond to GRIP- and EPICA-driven
           6\,km-resolution runs.}
  \label{fig:timeseries}
\end{figure*}

% fig:snapshots
\begin{figure*}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled surface topography (500\,m contours)
           corresponding to the ice volume extremes indicated on
           Fig.~\ref{fig:timeseries}. An ice cap persists over the Skeena
           Mountains (SM) during MIS~3. Note the occurence of spatial
           similarities despite large differences in timing.}
  \label{fig:snapshots}
\end{figure*}

% fig:mis2
\begin{figure*}
  \includegraphics{icemaps-mis2}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~2 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis2}
\end{figure*}

% fig:mis4
\begin{figure*}
  \includegraphics{icemaps-mis4}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~4 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis4}
\end{figure*}

% fig:duration
\begin{figure*}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,ka.
           Note the irregular colour scale. A contiguous ice cover spanning
           from the Alaska Range (AR) to the southern Coast Mountains (CM) and
           the Columbia and Rocky mountains (RM) exists for about 29\,ka in
           both simulations. The maximal extent of the ice sheet generally
           corresponds to relatively short durations of ice cover, but ice
           cover persists over the Skeena Mountains (SM) during most of the
           simulation.}
  \label{fig:duration}
\end{figure*}

% fig:warmbase
\begin{figure*}
  \includegraphics{warmbase}
  \caption{Modelled duration of warm-based ice cover during the last
           120\,ka. Long ice cover durations combined with basal
           temperatures at the pressure-melting point may explain the strong
           glacial erosional imprint of the Skeena Mountains (SM) landscape.
           Hatches indicate areas that were covered by cold ice only.}
  \label{fig:warmbase}
\end{figure*}

% fig:warmfrac
\begin{figure*}
  \includegraphics{warmfrac}
  \caption{Modelled fraction of warm-based ice cover during the ice-covered
           period. Note the dominance of warm-based conditions on the
           continental shelf and major glacial troughs of the coastal ranges.
           Hatches indicate areas that were covered by cold ice only.}
  \label{fig:warmfrac}
\end{figure*}

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) (top panel), and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent (bottom panel).}
  \label{fig:deglacseries}
\end{figure}

% fig:deglacshots
\begin{figure*}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) during the last deglaciation
           from the GRIP (top panels) and EPICA (bottom panels) simulations.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:deglacshots}
\end{figure*}

% fig:deglac
\begin{figure*}
  \includegraphics{deglac}
  \caption{Modelled age of the last deglaciation. Areas where the MIS~4 glacial
           advance exceeded the last glacial maximum advanced are marked in
           green. Hatches denote re-advance of mountain-centred ice caps and
           and the decaying ice sheet between 14 and 10\,ka., which is more
           pronounced in the GRIP-driven simulation.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:deglac}
\end{figure*}

% fig:lastflow
\begin{figure*}
  \includegraphics{lastflow}
  \caption{Modelled of the deglacial basal ice velocities. Hatches
           indicate areas that remain non-sliding throughout deglaciation
           (22.0--8.0\,ka), notably including the Interior Plateau (IP).
           Note the concentric patterns of deglacial flow in the Liard
           Lowland (LL).
           Sliding grid cells were distinguished from non-sliding grid cells
           using a velocity threshold of 1\,\unit{m\,yr^{-1}}.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:lastflow}
\end{figure*}

% fig:profiles-grip
\begin{figure}
  \includegraphics{profiles-grip}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the GRIP 6\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-grip}
\end{figure}

% fig:profiles-epica
\begin{figure}
  \includegraphics{profiles-epica}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the EPICA 6\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-epica}
\end{figure}

>>>>

% Copernicus manuscript
%\documentclass[tc, manuscript]{copernicus}

% Copernicus final print
\documentclass[tc]{copernicus}

@@

% =============================================================================
\begin{document}
% =============================================================================

@@

\begin{figure}
  \includegraphics{locmap}
  \caption{Relief map of northern North America showing a reconstruction of the
           areas once covered by the Cordilleran (CIS), Laurentide (LIS),
           Innuitian (IIS) and Greenland (GIS) ice sheets during the last
           18\,\unit{\chem{^{14}C}\,ka} (21.4\,cal\,ka)
           \citep{Dyke.2004}. The rectangular box denotes the location of the
           modelling domain used in this study. Major mountain ranges covered
           by the ice sheet include the Alaska Range (AR), the Wrangell and
           St.-Elias mountains (WSEM), the Selwyn and Mackenzie mountains
           (SMKM), the Skeena Mountains (SM), the Coast and Rocky
           Mountains (CRM) and the North Cascades (NC). Major depressions
           include the Liard Lowland (LL), the Interior Plateau of British
           Columbia (IP) and the Puget Lowland (PL). The background
           map consists of ETOPO1 \citep{Amante.Eakins.2009} and Natural Earth
           Data \citep{Patterson.Kelso.2014}.}
  \label{fig:locmap}
\end{figure}

@@

\begin{table*}
  \centering
  \caption{Parameter values used in the ice sheet model.}
  \label{tab:params}
  {\begin{tabular}{llrl}
    \tophline
    Not.    & Name & Value & Unit \\
    \middlehline

@@

\begin{figure}
  \includegraphics{atm}
  \caption{Monthly mean near-surface air temperature, precipitation and
           standard deviation of daily mean temperature for January and July
           from the North American Regional Reanalysis
           \citep[NARR;][]{Mesinger.etal.2006},
           used to force the ice sheet model. Note the
           strong contrasts in seasonality, timing of the precipitation peak,
           and temperature variability over the model domain, notably between
           coastal and inland regions.}
  \label{fig:atm}
\end{figure}

The PDD computation accounts for stochastic temperature variations by assuming
a normal temperature distribution of standard deviation $\sigma$ aroung the
expected value $T_m$. It is expressed by an error-function formulation
\citep{Calov.Greve.2005},
\begin{equation}
    \label{eqn:calovgreve}
    \mathrm{PDD} = \int_{t_1}^{t_2} \mathrm{d}t
        \left[\frac{\sigma}{\sqrt{2\pi}}
                \exp\left({-\frac{T_{m}^2}{2\sigma^2}}\right)
              + \frac{T_{m}}{2} \, \mathrm{erfc}
                \left(-\frac{T_{m}}{\sqrt{2}\sigma}\right)\right] \,,
\end{equation}
which is numerically approximated using week-long sub-intervals. In order to
account for the effects of spatial and seasonal variations of temperature
variability \citep{Seguinot.2013}, $\sigma$ is computed from daily temperature
values from the NARR, after excluding variability associated with the seasonal
cycle itself \citep[Fig.~\ref{fig:atm}, cf.][]{Seguinot.Rogozhina.2014}.
Degree-day factors for snow and ice melt are derived from
mass-balance measurements on contemporary glaciers from the Coast Mountains and
Rocky Mountains in British Columbia
\citep[Table~\ref{tab:params};][]{Shea.etal.2009}.

\begin{table*}[t]
  \caption{Palaeo-temperature proxy records and scaling parameters yielding
           temperature offset time-series used to force the ice sheet model
           through the last glacial cycle (Fig.~\ref{fig:timeseries}). $f$
           corresponds to the scaling factor adopted to yield last glacial
           maximum ice limits in the vicinity of mapped end moraines, and
           $T_{[32, 22]}$ refers to the resulting mean temperature anomaly
           during the period -32 to~-22~ka after scaling.}
  \label{tab:records}
  {\begin{tabular}{l|ccc|ccc|l}
    \tophline
    Record & Latitude & Longitude & Elev. & Proxy & $f$ & $T_{[32, 22]}$
           & Reference\\
    & & & (m~a.s.l) & & & (K) & \\
    \middlehline
    GRIP     &  72{\degree} 35' N  % 72.58 (decimal)
             &  37{\degree} 38' W  % 37.64 (decimal)
             & 3238\,m
             & \chem{\delta^{18}O}
             & 0.35 & -5.8{\degree}C  % -16.4126 (before scaling)
             & \citet{Dansgaard.etal.1993} \\

@@

Temperature offset time-series, ${\Delta}T_{TS}$, are derived from
palaeo-temperature proxy records from
the Greenland Ice Core Project \citep[GRIP,][]{Dansgaard.etal.1993}, the
North Greenland Ice Core Project \citep[NGRIP,][]{Andersen.etal.2004},
the European Project for Ice Coring in Antarctica \citep[EPICA,][]
{Jouzel.etal.2007}, the Vostok ice core \citep{Petit.etal.1999}, and Ocean
Drilling Program (ODP) sites 1012 and 1020, both located off the coast of
California \citep{Herbert.etal.2001}. Palaeo-temperatures from the GRIP and
NGRIP
records were calculated from oxygen isotope (\chem{\delta^{18}O}) measurements
using a quadratic equation \citep{Johnsen.etal.1995},
\begin{align}
    {\Delta}T_{TS}(t) = &-11.88 [\chem{\delta^{18}O}(t)
                                -\chem{\delta^{18}O}(0)] \nonumber \\
                        &-0.1925[\chem{\delta^{18}O}(t)^2
                                 -\chem{\delta^{18}O}(0)^2] \,,
\end{align}
while temperature reconstructions from Antarctic and oceanic cores were
provided as such. All records were scaled linearly (Table~\ref{tab:records}) in
order to simulate comparable ice extents at the LGM  (Table~\ref{tab:extrema})
and realistic outlines (Fig.~\ref{fig:snapshots}).

\begin{figure*}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and ocean records
           (Table~\ref{tab:records}) used as palaeo-climate forcing for the ice
           sheet model (top panel), and modelled ice volume (bottom panel)
           through the last 120\,ka. Ice volumes are expressed in meters of sea
           level equivalent (m~s.l.e.). Gray fields indicate Marine Oxygen
           Isotope Stage (MIS) boundaries for MIS~2 and MIS~4 according to a
           global compilation of benthic \chem{\delta^{18}O} records
           \citep{Lisiecki.Raymo.2005}. Hatched rectangles highlight the
           time-volume space for ice volume extremes corresponding to MIS~4
           (61.9--55.4\,ka), MIS~3 (52.2--45.6\,ka), and MIS~2 (LGM,
           29.5--16.9\,ka). Dotted lines correspond to GRIP- and EPICA-driven
           6\,km-resolution runs.}
  \label{fig:timeseries}
\end{figure*}

\begin{figure*}
  \includegraphics{snapshots}
  \caption{Snapshots of modelled surface topography (500\,m contours)
           corresponding to the ice volume extremes indicated on
           Fig.~\ref{fig:timeseries}. An ice cap persists over the Skeena
           Mountains (SM) during MIS~3. Note the occurence of spatial
           similarities despite large differences in timing.}
  \label{fig:snapshots}
\end{figure*}

\begin{table*}
  \caption{Extremes in Cordilleran ice sheet volume and extent corresponding to
           MIS~4, 3 and 2 for each of the six low-resolution simulations
           (Fig.~\ref{fig:timeseries}).}
  \label{tab:extrema}
  {\begin{tabular}{l*{3}{|ccc}}
    \tophline
             & \multicolumn{3}{c}{Age (ka)}
             & \multicolumn{3}{c}{Ice extent (\unit{10^6\,km^2})}
             & \multicolumn{3}{c}{Ice volume (m~s.l.e.)} \\
    Record   &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2
             &  MIS~4 &  MIS~3 &  MIS~2 \\
    \middlehline
    GRIP     &  57.58 &  49.24 &  19.52
             &   1.98 &   0.46 &   2.13
             &   7.52 &   0.89 &   8.52 \\
    NGRIP    &  60.26 &  50.16 &  22.85
             &   2.16 &   0.50 &   2.09
             &   8.69 &   0.93 &   8.24 \\
    EPICA    &  61.87 &  45.57 &  17.10
             &   1.57 &   0.95 &   2.08
             &   5.20 &   2.44 &   8.35 \\
    Vostok   &  60.87 &  49.68 &  16.87
             &   1.55 &   0.86 &   2.14
             &   5.10 &   2.01 &   8.66 \\
    ODP 1012 &  55.41 &  47.08 &  23.21
             &   1.44 &   0.85 &   2.13
             &   4.50 &   2.06 &   8.46 \\
    ODP 1020 &  60.16 &  52.24 &  29.46
             &   1.32 &   0.70 &   2.08
             &   3.88 &   1.52 &   8.32 \\
    \middlehline
    Minimum  &  61.87 &  52.24 &  29.46
             &   1.32 &   0.46 &   2.08
             &   3.88 &   0.89 &   8.24 \\
    Maximum  &  55.41 &  45.57 &  16.87
             &   2.16 &   0.95 &   2.14
             &   8.69 &   2.44 &   8.66 \\
    \bottomhline
  \end{tabular}}
  \belowtable{}
\end{table*}

\begin{figure*}
  \includegraphics{icemaps-mis2}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~2 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis2}
\end{figure*}

\begin{figure*}
  \includegraphics{icemaps-mis4}
  \caption{Modelled surface topography (200\,m contours) and surface velocity
           (colour mapping) corresponding to the maximum ice volume during
           MIS~4 in the GRIP and EPICA high-resolution simulations.}
  \label{fig:mis4}
\end{figure*}

\begin{figure*}
  \includegraphics{duration}
  \caption{Modelled duration of ice cover during the last 120\,ka.
           Note the irregular colour scale. A contiguous ice cover spanning
           from the Alaska Range (AR) to the southern Coast Mountains (CM) and
           the Columbia and Rocky mountains (RM) exists for about 29\,ka in
           both simulations. The maximal extent of the ice sheet generally
           corresponds to relatively short durations of ice cover, but ice
           cover persists over the Skeena Mountains (SM) during most of the
           simulation.}
  \label{fig:duration}
\end{figure*}

\begin{figure*}
  \includegraphics{warmbase}
  \caption{Modelled duration of warm-based ice cover during the last
           120\,ka. Long ice cover durations combined with basal
           temperatures at the pressure-melting point may explain the strong
           glacial erosional imprint of the Skeena Mountains (SM) landscape.
           Hatches indicate areas that were covered by cold ice only.}
  \label{fig:warmbase}
\end{figure*}

\begin{figure*}
  \vspace{-0.5mm}  % enough to allow the two figures to fit on one page
  \includegraphics{warmfrac}
  \caption{Modelled fraction of warm-based ice cover during the ice-covered
           period. Note the dominance of warm-based conditions on the
           continental shelf and major glacial troughs of the coastal ranges.
           Hatches indicate areas that were covered by cold ice only.}
  \label{fig:warmfrac}
\end{figure*}

\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) (top panel), and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent (bottom panel).}
  \label{fig:deglacseries}
\end{figure}

\begin{figure*}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,m contours)
           and surface velocity (colour mapping) during the last deglaciation
           from the GRIP (top panels) and EPICA (bottom panels) simulations.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:deglacshots}
\end{figure*}

\begin{figure*}
  \vspace{-1.5mm}  % enough to allow the two figures to fit on one page
  \includegraphics{deglac}
  \caption{Modelled age of the last deglaciation. Areas where the MIS~4 glacial
           advance exceeded the last glacial maximum advanced are marked in
           green. Hatches denote re-advance of mountain-centred ice caps and
           and the decaying ice sheet between 14 and 10\,ka., which is more
           pronounced in the GRIP-driven simulation.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:deglac}
\end{figure*}

\begin{figure*}
  \includegraphics{lastflow}
  \caption{Modelled of the deglacial basal ice velocities. Hatches
           indicate areas that remain non-sliding throughout deglaciation
           (22.0--8.0\,ka), notably including the Interior Plateau (IP).
           Note the concentric patterns of deglacial flow in the Liard
           Lowland (LL).
           Sliding grid cells were distinguished from non-sliding grid cells
           using a velocity threshold of 1\,\unit{m\,yr^{-1}}.
           Dashed segments indicate the location of profiles used in
           Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}.}
  \label{fig:lastflow}
\end{figure*}

\begin{figure}
  \includegraphics{profiles-grip}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the GRIP 6\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-grip}
\end{figure}

\begin{figure}
  \includegraphics{profiles-epica}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,ka) in the EPICA 6\,km
           simulation, corresponding to the four transects indicated in
           Figs.~\ref{fig:deglacshots}--\ref{fig:lastflow}.}
  \label{fig:profiles-epica}
\end{figure}

% tab:params

% tab:extrema
